MSTK: Mesh Toolkit, v 1.83

### 2016-01-19 docs/MSTK.tex
Added enum for gather operations on entity attributes

\item[]{\bf {\em int} MESH\_Num\_Vertices({\em Mesh\_ptr} mesh):}
Number of vertices in the mesh.

\item[]{\bf {\em int} MESH\_Num\_Edges({\em Mesh\_ptr} mesh):}
Number of edges in the mesh. For reduced representations, this routine
returns 0 since it is impractically expensive to count the number of
edges when they do not explicitly exist. Applications must find a way
to avoid using this routine for reduced representations.

\item[]{\bf {\em int} MESH\_Num\_Faces({\em Mesh\_ptr} mesh):}
Number of faces in the mesh. For reduced representations R1 or R2,
this routine counts only the faces that are explicitly represented
i.e. faces not connected to any mesh region. Therefore, a value of 0
will be returned for the number of faces of a tetrahedral mesh with
representation R1 or R2 but the correct number will be reported for a
tetrahedral mesh in other representations. Also, the correct number
will be reported for the number of faces in a surface mesh in
representation R1 or R2.  Therefore, this routine must be used
carefully.

\item[]{\bf {\em int} MESH\_Num\_Regions({\em Mesh\_ptr} mesh):}
Number of regions in the mesh.

@@

\item[]{\bf {\em MVertex\_ptr} MESH\_Vertex({\em Mesh\_ptr} mesh,
{\em int} i):} Return the i'th vertex in the mesh. Returns NULL if i
$<$ 0 or i $>$ number of mesh vertices.

\item[]{\bf {\em MEdge\_ptr} MESH\_Edge({\em Mesh\_ptr} mesh,
{\em int} i):} Return the i'th edge in the mesh. Returns NULL if i $<$
0 or i $>$ number of mesh edges. Returns NULL for reduced
representations.

\item[]{\bf {\em MFace\_ptr} MESH\_Face({\em Mesh\_ptr} mesh,
{\em int} i):} Return the i'th face in the mesh. Returns NULL if i $<$
0 or i $>$ number of mesh faces. Only faces explicitly represented in
the mesh are returned for reduced representation (See explanation for
MESH\_Num\_Faces).

\item[]{\bf {\em MRegion\_ptr} MESH\_Region({\em Mesh\_ptr} mesh, {\em
      int} i):} Return the i'th region in the mesh. Returns NULL if i
  $<$ 0 or i $>$ number of mesh region.

@@

\item[]{\bf {\em MVertex\_ptr} MESH\_Next\_Vertex({\em Mesh\_ptr}
    mesh, {\em int} *idx):} Returns the next vertex while iterating
  through the vertices of the mesh. See the routine {\bf
    List\_Next\_Entry} above for an explanation of how the iteration
  works. This routine is in general faster than using the routine {\bf
    MESH\_Vertex}.

\item[]{\bf {\em MEdge\_ptr} MESH\_Next\_Edge({\em Mesh\_ptr} mesh,
{\em int} *idx):} Returns the next edge while iterating through the
edges of the mesh. See the routine List\_Next\_Entry above for an
explanation of how the iteration works.  The routine always returns
NULL for reduced representations.

\item[]{\bf {\em MFace\_ptr} MESH\_Next\_Face({\em Mesh\_ptr} mesh,
{\em int} *idx):} Returns the next face while iterating through the
faces of the mesh. See the routine {\bf List\_Next\_Entry} above for
an explanation of how the iteration works.  Only faces explicitly
represented in the mesh are returned for reduced representation (See
explanation for {\bf MESH\_Num\_Faces}).

\item[]{\bf {\em MRegion\_ptr}
    MESH\_Next\_Region({\em Mesh\_ptr} mesh, {\em int} *idx):}
  Returns the next region while iterating through the regions of the
  mesh. See the routine {\bf List\_Next\_Entry} above for an
  explanation of how the iteration works.

>>>>

\item[]{\bf {\em int} MESH\_Num\_Vertices({\em Mesh\_ptr} mesh):}
Number of vertices in the mesh. This includes owned and ghost
vertices.

\item[]{\bf {\em int} MESH\_Num\_Edges({\em Mesh\_ptr} mesh):} Number
  of edges in the mesh (owned and ghost). For reduced representations,
  this routine returns 0 since it is impractically expensive to count
  the number of edges when they do not explicitly exist. Applications
  must find a way to avoid using this routine for reduced
  representations.

\item[]{\bf {\em int} MESH\_Num\_Faces({\em Mesh\_ptr} mesh):} Number
  of faces in the mesh (owned and ghost). For reduced representations
  R1 or R2, this routine counts only the faces that are explicitly
  represented i.e. faces not connected to any mesh region. Therefore,
  a value of 0 will be returned for the number of faces of a
  tetrahedral mesh with representation R1 or R2 but the correct number
  will be reported for a tetrahedral mesh in other
  representations. Also, the correct number will be reported for the
  number of faces in a surface mesh in representation R1 or R2.
  Therefore, this routine must be used carefully.

\item[]{\bf {\em int} MESH\_Num\_Regions({\em Mesh\_ptr} mesh):}
Number of regions in the mesh (owned and ghost).

@@

\item[]{\bf {\em MVertex\_ptr} MESH\_Vertex({\em Mesh\_ptr} mesh,
{\em int} i):} Return the i'th vertex in the mesh. Returns NULL if i
$<$ 0 or i $>$ number of mesh vertices. The vertex may be owned or ghost.

\item[]{\bf {\em MEdge\_ptr} MESH\_Edge({\em Mesh\_ptr} mesh, {\em
    int} i):} Return the i'th edge in the mesh. Returns NULL if i $<$
  0 or i $>$ number of mesh edges. The edge may be owned or
  ghost. Returns NULL for reduced representations.

\item[]{\bf {\em MFace\_ptr} MESH\_Face({\em Mesh\_ptr} mesh, {\em
    int} i):} Return the i'th face in the mesh. Returns NULL if i $<$
  0 or i $>$ number of mesh faces. The face may be owned or
  ghost. Only faces explicitly represented in the mesh are returned
  for reduced representation (See explanation for MESH\_Num\_Faces).

\item[]{\bf {\em MRegion\_ptr} MESH\_Region({\em Mesh\_ptr} mesh, {\em
    int} i):} Return the i'th region in the mesh. Returns NULL if i
  $<$ 0 or i $>$ number of mesh region. The region may be owned or
  ghost.

@@

\item[]{\bf {\em MVertex\_ptr} MESH\_Next\_Vertex({\em Mesh\_ptr}
  mesh, {\em int} *idx):} Returns the next vertex while iterating
  through the vertices of the mesh. The vertex may be owned or ghost
  and the type must be checked using {\bf MV\_PType}. See the routine
  {\bf List\_Next\_Entry} above for an explanation of how the
  iteration works. This routine is in general faster than using the
  routine {\bf MESH\_Vertex}.

\item[]{\bf {\em MEdge\_ptr} MESH\_Next\_Edge({\em Mesh\_ptr} mesh,
  {\em int} *idx):} Returns the next edge while iterating through the
  edges of the mesh. The edge may be owned or ghost
  and the type must be checked using {\bf ME\_PType}. See the routine
  List\_Next\_Entry above for an explanation of how the iteration
  works.  The routine always returns NULL for reduced representations.

\item[]{\bf {\em MFace\_ptr} MESH\_Next\_Face({\em Mesh\_ptr} mesh,
  {\em int} *idx):} Returns the next face while iterating through the
  faces of the mesh. The face may be owned or ghost
  and the type must be checked using {\bf MF\_PType}. See the routine
  {\bf List\_Next\_Entry} above for an explanation of how the
  iteration works.  Only faces explicitly represented in the mesh are
  returned for reduced representation (See explanation for {\bf
    MESH\_Num\_Faces}).

\item[]{\bf {\em MRegion\_ptr} MESH\_Next\_Region({\em Mesh\_ptr}
  mesh, {\em int} *idx):} Returns the next region while iterating
  through the regions of the mesh. The region may be owned or ghost
  and the type must be checked using {\bf MR\_PType}. See the routine
  {\bf List\_Next\_Entry} above for an explanation of how the
  iteration works.
